Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph\tnoteref{t1,t2}

### 2016-04-25 curvature.tex
revised degree change intro

In our next lemma, we characterize how the degree of a tree changes after an rSPR operation, showing that pairs of trees that are close in the graph can not achieve these extreme degree differences.
We show that the magnitude of the degree change depends solely on the size of the subtree to be moved, the difference between the depths of its original and new locations, and the size of its original and new neighboring subtrees.
This relation will allow us to improve the degree bounds between adjacent trees.
See Figure~\ref{fig:spr-degree-change} for an illustration of the lemma.

>>>>

These degree bounds apply only to arbitrary trees, and the maximum degree difference occurs between trees that differ by many SPR operations.
In our next lemma, we characterize how the degree of a tree changes after an rSPR operation.
This relation will allow us to improve the degree bounds between adjacent trees.
We show that the magnitude of the degree change depends solely on the size of the subtree to be moved, the difference between the depths of its original and new locations, and the size of its original and new neighboring subtrees.
See Figure~\ref{fig:spr-degree-change} for an illustration of the lemma.
